Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-09-13 fully-abstract-comp/technical-report.tex
updated permission hieararchy to no longer include wl permission

\subsection{Permissions}
\lau{23-03-2017: I am not sure we need the opaque capabilities anymore.} % I am not sure why I did not think the opaque capabilities where necessary, but I have a feeling we talked about this in Leuven and came to the conclusion that they were necessary.
\begin{figure}[!h]
  \centering
  \begin{tikzpicture}[main node/.style={}]
    \node[main node] (rwlx) {$\rwlx$};
    \node[main node] (rwx) [below of=rwlx] {$\rwx$};
    \node[main node] (rx) [below of=rwx] {$\rx$};
    \node[main node] (e) [below of=rx] {$\enter$};

    \node[main node] (rwlxo) [below right of=rwlx,yshift=-0.1cm] {$\rwlxo$};
    \node[main node] (rwxo) [below of=rwlxo] {$\rwxo$};
    \node[main node] (rxo) [below of=rwxo] {$\rxo$};
    \node[main node] (eo) [below of=rxo] {$\entero$};

    \node[main node] (rwl) [below left of=rwlx,xshift=-0.5cm,yshift=-0.3cm] {$\rwl$};
    \node[main node] (rw) [below of=rwl] {$\rw$};
    \node[main node] (r) [below of=rw] {$\readonly$};
    \node[main node] (0) [below of=r] {$\noperm$};

    \node[main node] (rwlo) [below right of=rwl,yshift=-0.1cm] {$\rwlo$};
    \node[main node] (rwo) [below of=rwlo] {$\rwo$};
    \node[main node] (ro) [below of=rwo] {$\ro$};
    \node[main node] (0o) [below of=ro] {$\nopermo$};

    \path[every node/.style={font=\sffamily\small}]
    (rwlxo) edge (rwxo)
    (rwxo) edge (rxo)
    (rxo) edge (eo)

    (rwl) edge (rw)
    (rw) edge (r)
    (r) edge (0)

    (rwlo) edge (rwo)
    (rwo) edge (ro)
    (ro) edge (0o)

    (rwlx) edge[dashed] (rwx)
    (rwx) edge[dashed] (rx)
    (rx) edge[dashed] (e)

    (rwlo) edge (rwlxo)
    (rwo) edge (rwxo)
    (ro) edge (rxo)
    (0o) edge (eo)

    (rwlo) edge (rwl)
    (rwo) edge (rw)
    (ro) edge (r)
    (0o) edge (0)

    (rwl) edge (rwlx)
    (rw) edge[dashed] (rwx)
    (r) edge[dashed] (rx)
    (0) edge[dashed] (e)

    (rwlxo) edge (rwlx)
    (rwxo) edge[dashed] (rwx)
    (rxo) edge[dashed] (rx)
    (eo) edge[dashed] (e);
  \end{tikzpicture}

>>>>

\subsection{Permissions}
\lau{23-03-2017: I am not sure we need the opaque capabilities anymore.} % I am not sure why I did not think the opaque capabilities where necessary, but I have a feeling we talked about this in Leuven and came to the conclusion that they were necessary.
\begin{figure}[!h]
  \centering
  \begin{tikzpicture}[main node/.style={}]
    \node[main node] (rwx) {$\rwx$};
    \node[main node] (rx) [below of=rwx] {$\rx$};
    \node[main node] (e) [below of=rx] {$\enter$};

    \node[main node] (rwxo) [below right of=rwx,yshift=-0.1cm] {$\rwxo$};
    \node[main node] (rxo) [below of=rwxo] {$\rxo$};
    \node[main node] (eo) [below of=rxo] {$\entero$};

    \node[main node] (rw) [below left of=rwx,xshift=-0.5cm,yshift=-0.3cm] {$\rw$};
    \node[main node] (r) [below of=rw] {$\readonly$};
    \node[main node] (0) [below of=r] {$\noperm$};

    \node[main node] (rwo) [below right of=rw,yshift=-0.1cm] {$\rwo$};
    \node[main node] (ro) [below of=rwo] {$\ro$};
    \node[main node] (0o) [below of=ro] {$\nopermo$};

    \path[every node/.style={font=\sffamily\small}]
    (rwxo) edge (rxo)
    (rxo) edge (eo)

    (rw) edge (r)
    (r) edge (0)

    (rwo) edge (ro)
    (ro) edge (0o)

    (rwx) edge[dashed] (rx)
    (rx) edge[dashed] (e)

    (rwo) edge (rwxo)
    (ro) edge (rxo)
    (0o) edge (eo)

    (rwo) edge (rw)
    (ro) edge (r)
    (0o) edge (0)

    (rw) edge (rwx)
    (r) edge[dashed] (rx)
    (0) edge[dashed] (e)

    (rwxo) edge (rwx)
    (rxo) edge[dashed] (rx)
    (eo) edge[dashed] (e);
  \end{tikzpicture}
